---
title: "A Book"
author: "Kittipos Sirivongrungson"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
output:
  bookdown::gitbook: default
  #bookdown::pdf_book: default
---

# Bookdown Test

This is my experimental test repo for creating [a bookdown website](https://bookdown.org/yihui/bookdown/usage.html).

## Usage

By default, bookdown merges all Rmd files by the order of filenames, e.g., 01-intro.Rmd will appear before 02-literature.Rmd. Filenames that start with an underscore _ are skipped. If there exists an Rmd file named index.Rmd, it will always be treated as the first file when merging all Rmd files.

### Render {#render}

```{r eval=FALSE}
# bookdown::render_book(".", "bookdown::gitbook")
bookdown::preview_chapter("index.Rmd")
```

### Live Preview

Live preview of the book can be done by

```{r eval=FALSE}
bookdown::serve_book()
```


<!-- If you need PDF output, uncomment bookdown::pdf_book above in YAML. You will need a LaTeX installation, e.g., https://yihui.name/tinytex/ -->
